Harmony: A Systems Programming Language and Model Checker

### 2022-01-28 paper/paper.tex
More on continuations in the paper

def acquire(lk):
    atomically:
        if lk->held:
            stop lk->blocked[len lk->blocked]
        else:
            lk->held = True

@@

The Harmony <{stop x}> expression stops the current thread and saves
its state in the variable <{x}>.  Another thread can resume the
thread using the statement <{go x r}>, which causes the original
thread to resume, with the <{stop x}> expression evaluating to the
value <{r}>.  \autoref{fig:continuation} shows another implementation
of the lock specification of \autoref{fig:synch}(a) using continuations,
where blocked threads are placed on a FIFO queue and released in
that order.  Besides synchronization and scheduling, continuations
also enable the implementation of a primitive such as Posix
\texttt{fork}.

>>>>

def acquire(lk):
    atomically:
        if lk->held:
            stop ?lk->blocked[len lk->blocked]
        else:
            lk->held = True

@@

<{:var:p}>
The Harmony <{save(e)}> expression returns a tuple containing <{e}>
and the current context.
Another thread can instantiate a context <{c}>
using the statement <{go c r}>, with the context
returning <{r}> from the <{save(e)}> expression.
This is similar to the C \texttt{setjmp/longjmp} construct.
Similar to <{save}>, the <{stop p}> expression saves the current
context in <{!p}>, where <{p}> is the address value of a shared variable.
Unlike <{save}>, the context is removed from the current set of
threads.
\autoref{fig:continuation} shows another implementation
of the lock specification of \autoref{fig:synch}(a) using continuations,
where blocked threads are placed on a FIFO queue and released in
that order.  Besides synchronization, scheduling, and exception handling,
continuations also enable the implementation of a primitive such as Posix
\texttt{fork} or the implementation of co-routines.
